\TheTitle

### 2017-07-15 paper/abstract.tex
Fixing spelling error

This paper make three contributions; a conversion from DAG to \mt, an
implemenation of a tool built on the \mt model, and a user study to
evaluate and validate the implementation and model.

>>>>

This paper make three contributions; a conversion from DAG to \mt, an
implementation of a tool built on the \mt model, and a user study to
evaluate and validate the implementation and model.
